### 2019-02-04 thesis_report/introduction.tex
intro updated

\section{Majoranas in a Josephson junction}
	\comment{Why are SNS junctions potentially better?}
	A more convincing case could be made if one could control the system in such a way that the presence of Majoranas can be turned on or off.
	This feature is realized in a relatively recent proposal by Pientka et. al~\cite{pientka_topological_2017}, where, instead of a nanowire, a two-dimensional strip of semiconductor is used.
	On each side of the strip a superconductor is placed, forming a Josephson junction.
	Taking advantage of the current-phase relationship existing in such a device, control of the current can be used to change the system from the trivial phase (no Majoranas), to the topological phase (does contain Majoranas).
	The system has additional advantages: it allows for Majorana's to be created at lower magnetic fields, it is more compatible with convential semiconductor technology, and the Josephson junction provides new ways to detect the topological phase of the system.

>>>>

\section{Majoranas in a Josephson junction}
	\comment{Why are SNS junctions potentially better?}
	A more convincing case could be made if one could control the system in such a way that the presence of Majoranas can be turned on or off.
	This feature is realized in a relatively recent proposal by Pientka et. al~\cite{pientka_topological_2017}, where, instead of a nanowire, a two-dimensional strip of semiconductor is used.
	On each side of the strip a superconductor is placed, forming a Josephson junction.
	Taking advantage of the current-phase relationship existing in such a device, control of the current can be used to change the system from the trivial phase (no Majoranas) to the topological phase (does contain Majoranas).
	The system has additional advantages: it allows for Majorana's to be created at lower magnetic fields, it is more compatible with convential semiconductor technology, and the Josephson junction provides new ways to detect the topological phase of the system.
